---
title: "chap3.13"
author: "hyojunahn"
date: "2017년 10월 9일"
output: html_document
---

#3.13

### (a) Using the rnorm() function, create a vector, x, containing 100 observations drawn from a N(0, 1) distribution. This represents a feature, X.

``` {r}

set.seed(123)
a <- rnorm(100)
a

```
.

.

seed를 1로 set 한다. 


* rnorm(n, mean = 0, sd = 1)

  + If mean or sd are not specified they assume the default values of 0 and 1, respectively.


### (b) Using the rnorm() function, create a vector, eps, containing 100 observations drawn from a N(0, 0.25) distribution i.e. a normal distribution with mean zero and variance 0.25.

``` {r}

b <- rnorm(100, mean = 0, sd = 0.25^0.5)
b

```



### (c) Using x and eps, generate a vector y according to the model Y = -1 + -0.5X + e. What is the length of the vector y? What are the values of β0 and β1 in this linear model?

``` {r}
c <- -1 + 0.5*a + b
c
length(c)
```
.

.

y의 길이는 100이다. β0 와 β1은 -1과 0.5이다.


### (d) Create a scatterplot displaying the relationship between x and y. Comment on what you observe.

``` {r}
plot(a,c)
```
.
.

.

 + It looks like a linear relationship. and + direction. 

### (e) Fit a least squares linear model to predict y using x. Comment on the model obtained. How do ˆ β0 and ˆ β1 compare to β0 and β1?

``` {r}
lm.fit <- lm(c~a)
summary(lm(c~a))

```


 + $\hat{beta_{0}} = -1.05140
 + $\hat{beta_{1}} = -0.47376
 + 실제 값과 근접하게 나온다. p-value 유효하다.
 
### (f) Display the least squares line on the scatterplot obtained in (d). Draw the population regression line on the plot, in a different color. Use the legend() command to create an appropriate legend.

``` {r}
plot(a,c)
abline(lm.fit, lwd=3, col=2)
abline(-1,0.5,lwd=3,col=3)
legend(-1, legend = c("model fit", "pop. regression"), col=2:3, lwd=3)
```



### (g) Now fit a polynomial regression model that predicts y using x and x2. Is there evidence that the quadratic term improves the model fit? Explain your answer.

``` {r}
lm.fit_sq = lm(c~a+I(a^2))
summary(lm.fit_sq)
```

 + a^2의 값이 유효하지 않다. 모델에 적용하는데 적절치 않다고 생각한다. 

### (h) Repeat (a)–(f) after modifying the data generation process in such a way that there is less noise in the data. The model (3.39) should remain the same. You can do this by decreasing the variance of the normal distribution used to generate the error term in (b). Describe your results.

``` {r}
eps2 <- rnorm(100, sd=0.1)  # prior sd was 0.5
y2 <- -1 + 0.5*a + eps2
fit.lm2 <- lm(y2 ~ a)
summary(fit.lm2)
plot(a, y2)
abline(-1, 0.5, col="blue")   # true regression
abline(fit.lm2, col="red")    # fitted regression
legend(x = c(-2,-0.5),
       y = c(-0.5,0),
       legend = c("population", "model fit"),
       col = c("blue","red"), lwd=2 )
```



### (i) Repeat (a)–(f) after modifying the data generation process in such a way that there is more noise in the data. The model(3.39) should remain the same. You can do this by increasing the variance of the normal distribution used to generate the error term in (b). Describe your results.


``` {r}
eps3 <- rnorm(100, sd=1)  # orig sd was 0.5
y3 <- -1 + 0.5*a + eps3
fit.lm3 <- lm(y3 ~ a)
summary(fit.lm3)
plot(a, y3)
abline(-1, 0.5, col="blue")   # true regression
abline(fit.lm3, col="red")    # fitted regression
legend(x = c(0,2),
       y = c(-4,-3),
       legend = c("population", "model fit"),
       col = c("blue","red"), lwd=2 )

```


### (j) What are the confidence intervals for β0 and β1 based on the original data set, the noisier data set, and the less noisy data set? Comment on your results.

``` {r}
confint(lm.fit)
confint(fit.lm2)
confint(fit.lm3)
```

